\documentclass{article}

\usepackage{fullpage,enumitem,amsmath,graphicx,amssymb}

\title{CS 224n Assignment \#3: Dependency Parsing}
\author{Heehoon Kim}
\date{}

\begin{document}

\maketitle

\section{Machine Learning \& Neural Networks}

\begin{enumerate}[label=(\alph*)]
\item
\begin{enumerate}[label=\roman*.]
\item Using momentum helps to cancel out fluctuation by bumps in the contour of a loss function and reinforce the vector component to downward direction.
\item Parameters with small gradients will get larger updates, which in turn accelerates convergence. Parameters with large gradients will slow down, so overshooting can be prevented.
\end{enumerate}
\item
\begin{enumerate}[label=\roman*.]
\item $\gamma$ should be $\frac{1}{1-p_{drop}}$ to maintain overall magnitude of values in the layer.
\item During evaluation, deterministic results are preferred.
\end{enumerate}
\end{enumerate}

\section{Neural Transition-Based Dependency Parsing}

\begin{enumerate}[label=(\alph*)]
\item Here are steps.
\begin{center}
\footnotesize
\begin{tabular}{c|c|c|c}
Stack & Buffer & New dependency & Transition \\
\hline
$\lbrack$ROOT$\rbrack$ & $\lbrack$I, parsed, this, sentence, correctly$\rbrack$ & & Initial Configuration \\
$\lbrack$ROOT, I$\rbrack$ & $\lbrack$parsed, this, sentence, correctly$\rbrack$ & & SHIFT \\
$\lbrack$ROOT, I, parsed$\rbrack$ & $\lbrack$this, sentence, correctly$\rbrack$ & & SHIFT \\
$\lbrack$ROOT, parsed$\rbrack$ & $\lbrack$this, sentence, correctly$\rbrack$ & parsed $\rightarrow$ I & LEFT-ARC \\
$\lbrack$ROOT, parsed, this$\rbrack$ & $\lbrack$sentence, correctly$\rbrack$ & & SHIFT \\
$\lbrack$ROOT, parsed, this, sentence$\rbrack$ & $\lbrack$correctly$\rbrack$ & & SHIFT \\
$\lbrack$ROOT, parsed, sentence$\rbrack$ & $\lbrack$correctly$\rbrack$ & sentence $\rightarrow$ this & LEFT-ARC \\
$\lbrack$ROOT, parsed$\rbrack$ & $\lbrack$correctly$\rbrack$ & parsed $\rightarrow$ sentence & RIGHT-ARC \\
$\lbrack$ROOT, parsed, correctly$\rbrack$ & $\lbrack$$\rbrack$ & & SHIFT \\
$\lbrack$ROOT, parsed$\rbrack$ & $\lbrack$$\rbrack$ & parsed $\rightarrow$ correctly & RIGHT-ARC \\
$\lbrack$ROOT$\rbrack$ & $\lbrack$$\rbrack$ & ROOT $\rightarrow$ parsed & RIGHT-ARC \\
\end{tabular}
\end{center}
\item At each step, one word goes from the buffer to the stack OR one word is popped from the stack. So it takes $2n$ steps.
\end{enumerate}

\begin{enumerate}[label=(\alph*),start=5]
\item Achieved UAS of 88.52 on the dev set and UAS of 89.11 on the test set.
\item
\begin{enumerate}[label=\roman*.]
\item
\begin{itemize}
\item \textbf{Error type}: Verb Phrase Attachment Error
\item \textbf{Incorrect dependency}: wedding $\rightarrow$ fearing
\item \textbf{Correct dependency}: heading $\rightarrow$ fearing
\end{itemize}
\item
\begin{itemize}
\item \textbf{Error type}: Coordination Attachment Error
\item \textbf{Incorrect dependency}: makes $\rightarrow$ rescue
\item \textbf{Correct dependency}: rush $\rightarrow$ rescue
\end{itemize}
\item 
\begin{itemize}
\item \textbf{Error type}: Prepositional Phrase Attachment Error
\item \textbf{Incorrect dependency}: named $\rightarrow$ Midland
\item \textbf{Correct dependency}: guy $\rightarrow$ Midland
\end{itemize}
\item 
\begin{itemize}
\item \textbf{Error type}: Modifier Attachment Error
\item \textbf{Incorrect dependency}: elements $\rightarrow$ most
\item \textbf{Correct dependency}: crucial $\rightarrow$ most
\end{itemize}
\end{enumerate}
\end{enumerate}



\end{document}